---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)


```

```{css}
body {font-family: Time;
background-color: #DBA4DB

}
h1 {color:#FFFFFF }

p {color:#F2F0F0}

```
# My Stats220 Dynamic Report 

I am investigating how often students check their canvas app, and at what point of the week they are more likely to check Canvas. 

Throughout this project I am looking at the way students utilise their access to their Canvas application, and from there I am able to analyse a pattern of how the application is being utilised.

**Below I have produced two graphs from my Google Form, where I surveyed 20 students.
Asking how often they check their Canvas application and at which point of the week they are likely to open their app and check Canvas.**


```{r} 
library(tidyverse)

#Part C

logged_data <- read.csv ("https://docs.google.com/spreadsheets/d/e/2PACX-1vQX49w3iLrJ4XtN4vOt-sEH1r7Zd5wJw0Za0jJr8stuKusWXslZ1jnv8qM-p-lt9F-FnSt6ycxQuLo9/pub?gid=601999998&single=true&output=csv")


latest_data <- logged_data %>% 
  rename(canvas_check = `How.often.do.you.check.your.canvas.application.on.a.daily.basis`,
         point_of_the_week = `At.what.point.in.the.week.are.you.more.likely.to.check.your.canvas.application`)

#mean check
mean_check <- round(mean(latest_data$canvas_check))


ggplot(data= latest_data) +
  geom_bar(aes(x = canvas_check),
           fill = "#FFC0CB" ) +
  labs(
    title = "How many times a day are you likely to open Canvas",
    x = "number of times canvas is opened",
    y = "count")

```

As shown in the first bar graph, a student is more likely on average to check their Canvas app 1-3 times a day during a semester.
The average amount of times a student will open canvas is `r mean_check`


```{r}


#dynamic comment
max_check <- latest_data %>%
  count(point_of_the_week) %>%
  slice_max(n,n =1)

#reviewed graph with Liza, seperated rows and changed the angle of the variables
latest_data %>% 
  select(point_of_the_week) %>% 
  separate_rows(point_of_the_week, sep = ", ") %>% 
  ggplot() +
  geom_bar(aes(x = point_of_the_week),
           fill =  "#89CFF0") +
  labs(
    title = "What point in the week are students more likely to check Canvas",
    x = "Point of the week") +
  scale_x_discrete(guide = guide_axis(angle = 90))


```

In my second bar graph I have highlighted the point within the week a student is more likely to check their Canvas app,
The highest surveyed point of the week was `r max_check`








